---
title: "Advance BA with R Project"
author: "Akash Chandrakar"
date: "May 6, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries

```{r}
library(C50)
library(tree)
library(caret)
library(AppliedPredictiveModeling)
library(pROC)
library(MASS)
library(glmnet)
library(nnet)
library(ggplot2)


```



Task 1: Explore the data
. Describe what the rows and columns of the data represent.
```{r}
data(churn)
str(churnTrain)
total <- rbind(churnTrain, churnTest)

```

. What is the overall churn rate?

```{r}

churn.table <- as.data.frame(table(total$churn))
churn.table$percentfreq <- churn.table$Freq/sum(churn.table$Freq)
churn.table

```

. Show some useful or interesting plots using ggplot.

```{r}
ggplot() + geom_bar(aes(y = ..count..,x =as.factor(international_plan),fill = as.factor(churn)),data=total)+labs(fill="Churn",x="International Plan",y="Frequency")

ggplot() + geom_bar(aes(y = ..count..,x =as.factor(voice_mail_plan),fill = as.factor(churn)),data=total)+labs(fill="Churn",x="Voice Mail Plan",y="Frequency")

ggplot() + geom_bar(aes(y = ..count..,x =as.factor(area_code),fill = as.factor(churn)),data=total)+labs(fill="Churn",x="Area Code",y="Frequency")+scale_x_discrete(labels=c("area_code_408" = "408","area_code_415" = "415","area_code_510" = "510"))
```


Task 2: Build an interpretable model and measure its performance

```{r}
churnTrain1 = churnTrain[,-c(1,3,4,5)]
churnTest1 = churnTest[,-c(1,3,4,5)]
churnTrain.x = churnTrain1[,-16] 
churnTrain.y = churnTrain1[,16]

zerovar.cols = nearZeroVar(churnTrain.x)
churnTrain.x = churnTrain.x[,-zerovar.cols]

numeric.y = rep( +1, length(churnTrain.y) )
numeric.y[churnTrain.y=="no"] = 0 
correlation.matrix = cor( cbind( churnTrain.x, numeric.y ))
corr.name = names( correlation.matrix[,15] )
corr.values = as.double( correlation.matrix[,15])
corr.values.df = data.frame(corr.values)
rownames(corr.values.df) = corr.name
colnames(corr.values.df) = c("correlation")
print( corr.values.df[ order(abs(corr.values.df$correlation)), , drop=FALSE ] )

ctrl = trainControl( summaryFunction=twoClassSummary, classProbs=TRUE )
xx =churnTrain1[,-c(3,6,9,12,16)]
y= churnTrain1[,16]
xx1 <- churnTest1[,-c(3,6,9,12,16)]
y1 <- churnTest1[,16]

set.seed(1001)
early.model = train( churnTrain1[,-16], y, method="glm", metric="ROC", family = "binomial", trControl=ctrl )
summary(early.model)
logistic.model = train( xx, y, method="glm", metric="ROC", family = "binomial", trControl=ctrl )
logistic.predictions = 1-predict( logistic.model, xx1, type="prob" )
logistic.roc = roc( response=y1, predictor=logistic.predictions[,1] )
summary(logistic.model)
plot(logistic.roc)

```

. What factors seem to be driving customer churn?

. Give an idea to mitigate churn based on this model? This can be a general policy or strategy proposal.

Task 3: Build the best tree-based predictive model you can and measure its performance

```{r}
churnTest.tree = churnTest[,-1]
churnTrain.tree = churnTrain[,-1]
tree.model <- tree(churn ~., data = churnTrain.tree)
summary(tree.model)
tree.predicted <- predict(tree.model, newdata = churnTest.tree, type = "class")
tree.cm <- print(confusionMatrix(tree.predicted, churnTest.tree$churn, dnn = c("Predicted", "Reference")))

set.seed(10001)
tree.validate <- cv.tree(object = tree.model, FUN = prune.misclass )
tree.validate
plot(x=tree.validate$size, y=tree.validate$dev, type="b")

tree.model.pruned <- prune.misclass(tree.model, best = 10)
tree.pruned.predicted <- predict(tree.model.pruned, newdata = churnTest.tree, type ="class" )
tree.cm2 <- print(confusionMatrix(tree.pruned.predicted, churnTest.tree$churn, dnn = c("Predicted", "Reference")))
```

